\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\setstretch{1}
\usepackage[english]{babel}
\usepackage[]{amssymb} 
%\usepackage[enable]{darkmode} 
\usepackage{amsmath, amsthm}
\usepackage{mdframed}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usetikzlibrary{pgfplots.fillbetween}  
\pgfplotsset{compat=1.17} 
\makeatletter
\newcommand{\tpmod}[1]{{\@displayfalse\pmod{#1}}}
\makeatother

\mdfdefinestyle{problemstyle}{
    innertopmargin=10pt,
    innerbottommargin=10pt,
    innerrightmargin=10pt,
    innerleftmargin=10pt,
    outerlinewidth=1pt,
    topline=true,
    bottomline=true,
    leftline=true,
    rightline=true
}

%custom enviroment for exercises
\newenvironment{exercise}{
    \begin{mdframed}[style=problemstyle]\textcolor{black}{}
}{
    \end{mdframed}
}


\title{TPHYS 121 Workshop Week 7}
\author{}
\date{\vspace{-15ex}}

\begin{document}
\maketitle

\section*{Module 4 Problems}
\subsection*{Exercise 1}
For each of the following let $g=10m/s^2$ unless otherwise stated.
\begin{exercise}
    A $5kg$ object is moving at a speed of $10m/s$
    \begin{enumerate}[label=\alph*]
        \item Calculate the total energy of the object. 
        \item How much work is required to bring the object to a stop? 
    \end{enumerate}
\end{exercise}

\subsection*{Exercise 2}
\begin{exercise}
    A $1.5kg$ cart moving at $4m/s$ collides with a $2.5kg$ cart initially
    at rest. After the collision, the two carts stick together and move as 
    one. 
    \begin{enumerate}[label=\alph*]
        \item Find the velocity of both carts after the collision.
        \item Calculate the total kinetic energy before and after the
            collision. Is the kinetic energy conserved?
    \end{enumerate}
\end{exercise}

\subsection*{Exercise 3}
\begin{exercise}
    A basketball with mass $m$ is dropped from a hieght of $10m$. It hits
    the floor and bounces back.
    \begin{enumerate}
        \item Assuming the collision is perfectly elastic, what is the 
            max height of the ball after it bounces.
        \item What is the velocity of the basketball right before it hits 
            floor.
        \item what is the velocty of the basketball when it is at it's
            max hieght(after the bounce).
    \end{enumerate}
\end{exercise}


\section*{Additional Resources}
\begin{itemize}
    \item Flipping Physics on youtube: 
        \url{https://www.youtube.com/user/flippingphysics} 
\end{itemize}
\end{document}
